Untitled Draft

### 2023-03-15 doc/manuscript.Rmd
Fix demographic table reference
One sentence per line.
Abstract model_list to include other moderators. Add sex.

```{r load-targets, include=FALSE}
tar_load(model_list)
tar_load(data_clean)
tar_load(purdy_pictures)
pretty <- function(x) format(x, big.mark = ",")
```

@@

The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r length(unique(data_clean$participant_id)) |> pretty()` unique participants. Table \@ref(demo-participants) shows demographic information for all participants. A table of study characteristics can be found in supplementary materials.

@@

sleep_outcomes_by_PA_volume <- lapply(model_list[sleep_names], function(x){
tab <- format_table(x$table)  
tab
})

@@

sleep_outcomes_by_PA_intens <- lapply(model_list[sleep_names], function(x){
tab <- format_table(x$table)  
tab
})

@@

PA_by_sleep_duration <- lapply(model_list[var_names], function(x){
tab <- format_table(x$table)  
tab
})

@@

PA_by_sleep_efficiency <- lapply(model_list[var_names], function(x){
tab <- format_table(x$table)  
tab
})

@@

PA_by_sleep_onset <- lapply(model_list[var_names], function(x){
tab <- format_table(x$table)  
tab
})

@@

PA_by_sleep_regularity <- lapply(model_list[var_names], function(x){
tab <- format_table(x$table)  
tab
})

>>>>

```{r load-targets, include=FALSE}
tar_load(model_list_by_age)
tar_load(data_clean)
tar_load(purdy_pictures)
pretty <- function(x) format(x, big.mark = ",")
```

@@

The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r length(unique(data_clean$participant_id)) |> pretty()` unique participants.
Table \@ref(tab:demo-participants) shows demographic information for all participants.
A table of study characteristics can be found in supplementary materials.

@@

sleep_outcomes_by_PA_volume <- lapply(model_list_by_age[sleep_names], function(x){
tab <- format_table(x$table)  
tab
})

@@

sleep_outcomes_by_PA_intens <- lapply(model_list_by_age[sleep_names], function(x){
tab <- format_table(x$table)  
tab
})

@@

PA_by_sleep_duration <- lapply(model_list_by_age[var_names], function(x){
tab <- format_table(x$table)  
tab
})

@@

PA_by_sleep_efficiency <- lapply(model_list_by_age[var_names], function(x){
tab <- format_table(x$table)  
tab
})

@@

PA_by_sleep_onset <- lapply(model_list_by_age[var_names], function(x){
tab <- format_table(x$table)  
tab
})

@@

PA_by_sleep_regularity <- lapply(model_list_by_age[var_names], function(x){
tab <- format_table(x$table)  
tab
})
